### 2014-03-12 src/methodology.Rnw
update

\section{Methodology}
\label{sec:methodology}
Our selection of programs was driven by a few overriding concerns. Our primary
requirement was that, our results had to be as widely applicable as possible
for real-world programs. Secondly, we strived for a statistically significant
result, reducing the amount of variables present in the experiments. For this
reason we chose a random sample of Java projects from Github\cite{github}
that uses the popular maven\cite{maven} build system, that has been used
elsewhere\cite{gopinath2014code}. This set of projects comes in two flavors
of test-suites. The original test-suites present in a limited number of
projects, and automatically generatd test-suites using randoop.  Due to the
constraints in resources, we had to further reduce the programs and test-suites
to those that could finish the mutation run in 10 minutes. From this set
of test-suites, we sampled 110 suites each for both original and randoop
generated test-suiets. This gave us 81 unique projects for both original
and randoop, and remaining projects having both flavors of test suites.

We ran mutation analysis on this set of projects using
PIT\cite{pitest}. However, since the operators provided by PIT are limited,
we extended PIT to provide newer operators that are similar to operators
provided by other mutation systems. The set of operators provided by PIT
are provided in Table~\ref{tbl:pitop}.

@@

\begin{table}[h]\footnotesize
\begin{tabular}{ll}
\hline \hline \\
\pitic & Invert negatives \\
\pitrv & Change return values \\
\pitm & Modify arithmetic operators\\
\pitvmc & Remove void method calls \\
\pitnc & Negate conditional statements \\
\pitcb & Modify boundary conditions \\
\piti & Modify increment/decrement \\
\pitnvmc & Replace non-void method calls \\
\pitcc & Replace constructor calls \\
\pitic & Replace inline constants \\
\piti & Remove increment/decrement \\
\pitemv & Replace member variable assignments \\
\pites & Modify switch statements \\
\pitrs & Remove switch elements* \\
\pitrc & Make conditionals true \\
\pitnc & Make conditionas false* \\
\hline
\end{tabular}
\caption{PIT Mutation Opeators (We have used abbreviations instead of operator names.)}
\label{tbl:pitop}
\end{table}

>>>>

\section{Methodology}
\label{sec:methodology}
Our selection of programs was driven by a few overriding concerns. Our primary
requirement was that, our results had to be as widely applicable as possible
for real-world programs. Secondly, we strived for a statistically significant
result, reducing the amount of variables present in the experiments. For this
reason we chose a random sample of Java projects from Github\cite{github}
that uses the popular maven\cite{maven} build system, that has been used
elsewhere\cite{gopinath2014code}. We utilize two flavors of
of test-suites. The original test-suites present in a limited number of
projects, and automatically generatd test-suites using randoop.  Due
limited resources, we had to further reduce the programs and test-suites
to those that could finish the mutation run in 10 minutes. From this set
of test-suites, we sampled 110 suites each for both original and randoop
generated test-suiets. This gave us 81 unique projects for both original
and randoop, and remaining projects having both flavors of test suites.

We ran mutation analysis on this set of projects using
PIT\cite{pitest}. However, since the operators provided by PIT are limited,
we extended PIT to provide newer operators that are similar to operators
provided by other mutation systems. The set of operators that we used
are provided in Table~\ref{tbl:pitop}. For a detailed description of each,
please see~\cite{pitmut}

@@

\begin{table}[h]
\small{
\begin{tabular}{ll}
\hline \hline \\
\pitin & Remove negative sign from numbers\\
\pitrv & Mutate return values\\
\pitm & Mutate arithmetic operators\\
\pitvmc & Remove void method calls\\
\pitnc & Negate conditional statements\\
\pitcb & Modify boundaries in logical conditions\\
\piti & Modify increment and decrement statements\\
\pitnvmc & Remove non-void method calls, returning default value \\
\pitcc & Replace constructor calls, returning null \\
\pitic & Replace inline constants with default value \\
\pitri & Remove increment and decrement statements \\
\pitemv & Replace member variable assignments with default value \\
\pites & Modify switch statements \\
\pitrs & Replace switch labels with default (thus removing them) \\
\pitrc & Replace boolean conditions with true\\
\pitnc & Replace boolean conditions with false\\
\hline
\end{tabular}
}
\caption{PIT Mutation Opeators (We have used abbreviations instead of operator names.)}
\label{tbl:pitop}
\end{table}
